Roster Review (Generic)

### 2019-05-04 rosterReview_generic.Rmd
Minor notes and visual options

proj_batter <- add_z_scores_to_projections("data/depthChartProjections_ros_batters_20190422.csv","batter") 
proj_pitcher <- add_z_scores_to_projections("data/depthChartProjections_ros_pitchers_20190422.csv", "pitcher")

@@

#TODO save these to some file
projections$Name[projections$Name == 'Enrique Hernandez'] <- "Kike Hernandez"
projections$Name[projections$Name == 'Peter Alonso'] <- "Pete Alonso"
projections$Name[projections$Name == 'Joshua James'] <- "Josh James"

@@

```{r}
#TODO abstract some of these views
rosters_with_adj_projections %>% 
  mutate(zar = round(zar)) %>% 
  filter((team == 'Free Agent' & zar >=0) | (grepl("Plouffe",team) & zar < 0)) %>% 
  ggplot(aes(x=team,y=zar,color=type)) +
  geom_jitter(aes(text=glue("{name_full} - {display_position}", color=type))) +
  coord_flip() -> pa

@@

```{r}
# TODO find way to wrap these three views into one
rosters_with_adj_projections %>% 
  filter(grepl("Plouffe|Poofer",team)) %>% 
  select(team, manager, name_full, display_position, zar) %>% 
  arrange(zar %>% desc) %>% 
  View()
  # mutate(zar = janitor::round_half_up(zar)) %>% 
  # write_csv("data/tradeReview_20190423.csv")

rosters_with_adj_projections %>% 
  filter(grepl("Plouffe|Poofers",team)) %>% 
  ggplot(aes(x=team,y=zar,color=type)) +
  geom_jitter(aes(text=glue("{name_full} - {display_position}", color=type)), width=.2) +
  coord_flip() -> tv

@@

rosters_with_adj_projections %>% 
  filter(grepl("Plouffe|Poofer",team)) %>% 
  select(team, manager, name_full, display_position, zar) %>% 
  filter(grepl("Bregman|deGrom|Lindor",name_full)) %>% 
  group_by(team) %>% 
  summarize(zar = sum(zar))
```

```{r}
rosters_with_adj_projections %>% 
  filter(!grepl("Free Agent",team),
         grepl("SP|3B",display_position)) %>% 
  ggplot(aes(x=team,y=zar,color=type)) +
  geom_jitter(aes(text=name_full), width = .2) +
  coord_flip() -> tb

@@

```{r}
#TODO measuring projected value of draft picks, move to separate research
rosters_with_adj_projections %>% 
  filter(!is.na(draft_pick)) %>% 
  group_by(draft_round) %>% 
  summarize(zar_median = median(zar) %>% janitor::round_half_up(),
            zar_mean = mean(zar) %>% janitor::round_half_up()) %>%
  ggplot(aes(x=draft_round,y=zar_mean)) +
  geom_col() +
  geom_line(aes(y=zar))

>>>>

proj_batter <- add_z_scores_to_projections("data/depthChartProjections_ros_batters_20190429.csv","batter") 
proj_pitcher <- add_z_scores_to_projections("data/depthChartProjections_ros_pitchers_20190429.csv", "pitcher")

@@

#TODO save these to some file
projections$Name[projections$Name == 'Enrique Hernandez'] <- "Kike Hernandez"
projections$Name[projections$Name == 'Peter Alonso'] <- "Pete Alonso"
projections$Name[projections$Name == 'Joshua James'] <- "Josh James"
projections$Name[projections$Name == 'Shin-Soo Choo'] <- "Shin-soo Choo"

@@

```{r}
#TODO abstract some of these views
#FIXME some join issues here
rosters_with_adj_projections %>% 
  mutate(zar = round(zar)) %>% 
  filter((team == 'Free Agent' & zar >=0) | (grepl("Plouffe",team) & zar < 0)) %>% 
  ggplot(aes(x=team,y=zar,color=type)) +
  geom_jitter(aes(text=glue("{name_full} - {display_position}", color=type))) +
  coord_flip() -> pa

@@

```{r}
# TODO find way to wrap these three views into one
rosters_with_adj_projections %>% 
  filter(grepl("Plouffe|Hebrew",team)) %>% 
  select(team, manager, name_full, display_position, zar) %>% 
  arrange(zar %>% desc) %>% 
  View()
  # mutate(zar = janitor::round_half_up(zar)) %>% 
  # write_csv("data/tradeReview_20190423.csv")

rosters_with_adj_projections %>% 
  filter(grepl("Plouffe|Hebrew",team)) %>% 
  ggplot(aes(x=team,y=zar,color=type)) +
  geom_jitter(aes(text=glue("{name_full} - {display_position}", color=type)), width=.2) +
  coord_flip() -> tv

@@

rosters_with_adj_projections %>% 
  filter(grepl("Plouffe|Hebrew",team)) %>% 
  select(team, manager, name_full, display_position, zar) %>% 
  filter(grepl("deGrom|Rizzo",name_full)) %>% 
  group_by(team) %>% 
  summarize(zar = sum(zar))
```

```{r}
rosters_with_adj_projections %>% 
  filter(!grepl("Free Agent",team),
         # grepl("SP|3B",display_position)
         ) %>% 
  ggplot(aes(x=team,y=zar,color=type)) +
  geom_boxplot() +
  # geom_jitter(aes(text=name_full), width = .2) +
  coord_flip() -> tb

@@

```{r}
#TODO measuring projected value of draft picks, move to separate research
rosters_with_adj_projections %>% 
  filter(!is.na(draft_pick)) %>%
  group_by(draft_round) %>% 
  summarize(zar_median = median(zar) %>% janitor::round_half_up(),
            zar_mean = mean(zar) %>% janitor::round_half_up()) %>%
  ggplot(aes(x=draft_round,y=zar_mean)) +
  geom_col() +
  geom_line(aes(y=zar_median))
